% resume.tex
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=7.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large \hspace{2.5in} Andrew Gapic}\\ \textbf{\hspace{2.4in}2A Software Engineering}\\\hspace{0.3in} andrewjdg@gmail.com  \hspace{0.5in}  andrewgapic.com   \hspace{0.5in}github.com/agapic \hspace{0.5in} 905-870-9478
\end{tabular*}
\\



\begin{description}
\item[Languages:]
Javascript, SQL, Python, Java, C/C++, HTML/CSS, PHP
\vspace{-0.09in}
\item[Technologies:]
Linux (Ubuntu, Kali), UNIX, Git, SVN, PostgreSQL, Oracle, Node.js, Handlebars.js, Parse, Grails, \\
\hspace{0.64in}Android Studio, Bootstrap, IntelliJ, Burp Suite, IDA, Brackets, jQuery, Angular.js, Dokku
\vspace{-0.09in}
\item[Interests:]
Information Security, Web Applications, Varsity Track and Field, Powerlifting, Toastmasters
\end{description}
\vspace{-0.3in}
\resheading{Experience}
\begin{itemize}
\item
\vspace{-0.17in}
	\ressubheading{Canadian Blood Services}{Ottawa, ON}{Software Developer}{May 2015 - Sept. 2015}
	\begin{itemize}
		\resitem{Developed and designed a Grails web application from scratch; migrated Lotus Notes data to Oracle and set up a relational database as the backend.}
		\resitem{Created user cases and continuously prototyped applications using the agile development methodology.}
		\resitem{Implemented the Google Maps API on several applications and solved a critical SSL certification issue.}
	\end{itemize}
\item
	\ressubheading{Tech Retreat}{Waterloo, ON}{Organizer}{April 2015 - Present}
	\begin{itemize}
		
		\resitem{Organized and planned a summer hackathon and learnathon for over 150 high school students.}
		\resitem{Coordinated event logistics and facilitated team work and discussion between participants.}
		\resitem{Created "capture the flags" to demonstrate the importance of security in web applications. Code available on Github.}
	\end{itemize}
\item
	\ressubheading{State Street}{Toronto, ON}{Pricing Specialist}{Sept. 2013 - Sept. 2014}
	\begin{itemize}
		
		\resitem{Designed several applications using VBA, increasing productivity by over 50\%.}
		\resitem{Performed due diligence on potentially incorrectly priced securities using the Bloomberg and Reuters pricing terminals.}
	\end{itemize}



\end{itemize}
\vspace{-0.3in}
\resheading{Side Projects}
\begin{itemize}
\item
\vspace{-0.17in}
		\ressubheading{Abracadabra}{}{http://abra.andrewgapic.com}{Aug. 2015 - Sept. 2015}
	\begin{itemize}
		\resitem{Wrote a Node.js web application that analyzes major gameplay changes for League of Legends using a sample size of 400,000 matches.}
		\resitem{Designed the frontend using HTML, CSS, jQuery, and Handlebars.js.}
		\resitem{Implemented the backend by storing 400,000 API requests in a PostgreSQL database and deployed the application using Dokku.}
		\resitem{Code available at https://www.github.com/agapic/abracadabra}
	\end{itemize}
\item
		\ressubheading{The North Bank}{}{https://github.com/agapic/HTN-2015-ARG}{May 2015 - Aug. 2015}
	\begin{itemize}
		\resitem{The North Bank is a CTF created for Hack the North with a team of four people.}
		\resitem{Implemented a tree of six servers as nodes which held a public key (or flags). Key concepts involved include integer overflow, TCP/IP, the Shellshock exploit, hash functions, and race conditions.}
\end{itemize}
\item
		\ressubheading{Flickr Photo Collector}{}{https://github.com/agapic/PhotoCollector}{Jan. 2015}
	\begin{itemize}
		\resitem{Developed an Android application utilizing MVC that displays Flickr's most recent photos using Loopers and Handlers.}
		\resitem{Utilized Android's HTTP networking to parse and display photo captions with the REST API.}

\end{itemize}

\end{itemize}
\vspace{-0.3in}

\resheading{Education}
\begin{itemize}
\item\vspace{-0.17in}
	\ressubheading{University of Waterloo}{Waterloo, ON}{Candidate for Bachelor of Software Engineering}{Sept. 2014 - Present}



\end{itemize}

\end{document}